{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-24 paper.tex
Minor rewrite of the 'difference with middlewares' section

Like traditional robotic middleware, \uwds offers a form of distributed
computation based on message passing. However, it distinguishes itself from
existing middleware in several significant ways.

First and foremost, \uwds purposefully does not offer any \emph{general}
capability to distribute computation and data flow amongst independent
components: it focusses specifically on distributing environment models, both
spatial (geometric models) and temporal (events and situations).

>>>>

Like traditional robotic middleware, \uwds offers a form of distributed
computation based on message passing. However, it distinguishes itself from
existing middleware in significant ways. Most importantly, \uwds purposefully
does not offer any \emph{general} capability to distribute computation and data
flow amongst independent components: it focusses specifically on distributing
environment models, both spatial (geometric models) and temporal (events and
situations). In that sense, \uwds really is a \emph{distributed datastructure}
with a narrow focus on the needs of spatio-temporal representations.
